CODEBOOK
Coursera: Getting and Cleaning Data

Author: Jeroen Kromme
Date: 11-08-2014

Input files:
```{r, echo = FALSE}
for (i in list.files(".")){ cat('- ',i, '\n')}
for (i in list.files("./data")){ cat('- ',i, '\n')}
for (i in list.files("./data/train")){ cat('- ',i, '\n')}
for (i in list.files("./data/test")){ cat('- ',i, '\n')}

```

Analysis script:
- run_analysis.R

Goal of script:
Tidy up data so it is unified workable dataset on which analyses can easily performed.

Tidy data has:
- each variable in a seperate column
- each observation in a seperate row
- there should be one table for each kind of variable
- include variable names
- variable names should be readable
- general data should be saved in one file per table

Actions in script:
- Load Packages
- Load data
- Naming variables (bulletpoint 4)
- Union datasets (bulletpoint 1)
- Only means and standard deviations (bulletpoint 2)
- Merge activity names to increase readibilty (bulletpoint 3)
- Join xdata and ydata 
- Tidy-up names
- Mean of each activity per subject (bulletpoint 5)
- Write files

Output files:
- cleanDataset.csv
- dataset_tidy.csv

Variables in cleanDataset:
```{r, echo = FALSE}
dataset <- read.csv( 'cleanDataset.csv')
for (i in names(dataset)[2:length(names(dataset))]){
  name = ''
  if (grepl('subject', i)){name ='id of subject'}
  else if (grepl('activityName', i)){name ='name of activity'}
  if (grepl('Avg', i)){name = paste0(name, 'mean of ')}
  else if (grepl('Std', i)){name = paste0(name, 'Standard deviation of ')} 
  if (grepl('Body', i)){name = paste0(name, 'body of ')} 
  else if (grepl('Gravity', i)){name = paste0(name, 'gravity of')}
  if (grepl('AccJerkMag', i)){name = paste0(name, 'magnitude of acceleration jerk ')} 
  else if (grepl('AccJerk', i)){name = paste0(name, 'acceleration jerk ')} 
  else if (grepl('AccMag', i)){name = paste0(name, 'magnitude of acceleration ')} 
  else if (grepl('Acc', i)){name = paste0(name, 'acceleration ')} 
  else if (grepl('GyroJerkMag', i)){name = paste0(name, 'magnitude of gyro jerk ')}
  else if (grepl('GyroJerk', i)){name = paste0(name, 'gyro jerk ')}
  else if (grepl('GyroMag', i)){name = paste0(name, 'magnitude of gyro ')}
  else if (grepl('Gyro', i)){name = paste0(name, 'gyro ')}
  if (grepl('.X', i)){name = paste0(name, 'of X')}
  else if (grepl('.Y', i)){name = paste0(name, 'of Y')}
  else if (grepl('.Z', i)){name = paste0(name, 'of Z')}
  cat('\n- ',i,':', name, ', type =', class(i))
  }

```


